A full approximation scheme multilevel method \\ for nonlinear variational inequalities

### 2024-01-09 paper/fascd.tex
had not noticed before now that Ciarlet states K_h (notsubset) K too

While \eqref{eq:fe:vi} approximates \eqref{eq:vi}, we warn the reader that it is usually not a conforming FE method.  That is, even if quadrature and other implementation details for $f^J$ are ignored, and despite the vector space inclusion $\mathcal{V}^J \subset \mathcal{V}$, from definitions \eqref{eq:originalconstraintset} and \eqref{eq:fe:fineconstraintset} we do not expect $\mathcal{K}^J \subset \mathcal{K}$ in general.  Even for continuous obstacles $\underline{\gamma}, \overline{\gamma}$, FE admissibility \eqref{eq:fe:fineconstraintset} will generally not imply $\mathcal{K}$-admissibility \eqref{eq:originalconstraintset}.  For a practical consequence of this situation, regarding Example \ref{ex:sia}, nodal bed elevation data in a glacier application will miss the topographic detail between the nodes \cite{Bueler2016}.

>>>>

While \eqref{eq:fe:vi} approximates \eqref{eq:vi}, we warn the reader that it is usually not a conforming FE method.  That is, even if quadrature and other implementation details for $f^J$ are ignored, and despite the vector space inclusion $\mathcal{V}^J \subset \mathcal{V}$, from definitions \eqref{eq:originalconstraintset} and \eqref{eq:fe:fineconstraintset} we do not expect $\mathcal{K}^J \subset \mathcal{K}$ in general \cite[section 5.1]{Ciarlet2002}.  Even for continuous obstacles $\underline{\gamma}, \overline{\gamma}$, FE admissibility \eqref{eq:fe:fineconstraintset} will generally not imply $\mathcal{K}$-admissibility \eqref{eq:originalconstraintset}.  For a practical consequence of this situation, regarding Example \ref{ex:sia}, nodal bed elevation data in a glacier application will miss the topographic detail between the nodes \cite{Bueler2016}.
